---
title: "guardianship asia"
format: html
editor: visual
---

## Overview

This file analyzes support for guardianship democracy in six East and Southeast Asian democracies (Japan, the Philippines, South Korea, Taiwan, Mongolia, and Indonesia), using World Values Survey (WVS) and Varitaies of Democracy (V-dem) data. It includes five main sections:

-   **System Support**: Measures weighted support for four regime types (democracy, rule by experts, military rule, strong leader) across countries and time, highlighting liberal democracies. `@fig-wvs-support`
-   **V-Dem (Electoral)**: Visualizes changes in the V-Dem Electoral Democracy Index (v2x_polyarchy) from 1945 to 2020 for the five focal countries. `@fig-vdem-plot`
-   **Guardianship Support**: Calculates and plots co-endorsement of democracy with each elite-led alternative (Dahlian, military, strongman) to capture guardianship democracy variants. `@fig-guardianship`
-   **Generational Analysis**: Classifies respondents into political generations based on democratic transitions and examines age- and generation-based differences in regime support. `@fig-gen-plot`
-   **Emancipative values**: Analyzes political values using the Emancipative Values Index (EVI) for democratic generations across cases. `@fig-gen-eman-plot`

All plots use post-stratification weights and highlight the six focal cases with distinct colors. Figures are saved to the `figures/` folder for integration into the manuscript.

## Load libraries ad data

```{r}

library(dplyr)
library(ggplot2)
library(scales)
library(stringr)
library(vdemdata)
library(tidyr)
library(ggthemes)
library(forcats)

# Load WVS data and tidy
wvsdf <- `WVS_Time_Series_1981-2022_rds_v5_0` %>% haven::zap_labels()


```

## System support

```{r}

#| echo: false

# Recode binary evaluations for "very good" or "fairly good" (1/2)
# E114 = Strong Leader
# E115 = Rule by Experts
# E116 = Military Rule
# E117 = Democracy

binary_cols <- c("E114", "E115", "E116", "E117")
weight_col <- "S017"

wvs_eval <- wvsdf %>%
  mutate(across(all_of(binary_cols), ~ ifelse(. %in% c(1, 2), 1, 0)))

# Add V-Dem regime classification
latest_year <- max(vdem$year, na.rm = TRUE)
vdem_classification <- vdem %>%
  filter(year == latest_year) %>%
  select(COUNTRY_ALPHA = country_text_id, v2x_regime) %>%
  mutate(regime_category = if_else(v2x_regime == 3, "Liberal Democracy", "Other"))

wvs_eval <- wvs_eval %>%
  left_join(vdem_classification, by = "COUNTRY_ALPHA")

# Calculate weighted proportions
proportions <- wvs_eval %>%
  filter(!is.na(S020)) %>%
  group_by(COUNTRY_ALPHA, S020) %>%
  summarise(
    across(
      all_of(binary_cols),
      ~ if (sum(!is.na(.x)) == 0) NA_real_ else weighted.mean(.x, w = .data[[weight_col]], na.rm = TRUE),
      .names = "Proportion_{col}"),
    .groups = "drop") %>%
  pivot_longer(
    cols = starts_with("Proportion_"),
    names_to = "Variable",
    values_to = "Proportion"
  ) %>%
  filter(Proportion > 0) %>%
  mutate(
    Variable = str_remove(Variable, "Proportion_"),
    Variable_Label = case_when(
      Variable == "E114" ~ "Strong Leader",
      Variable == "E115" ~ "Experts Rule",
      Variable == "E116" ~ "Army Rule",
      Variable == "E117" ~ "Democracy Good",
      TRUE ~ Variable
    )
  )

# Add highlight group
highlight_map <- wvs_eval %>%
  select(COUNTRY_ALPHA, regime_category) %>%
  distinct()

proportions <- proportions %>%
  left_join(highlight_map, by = "COUNTRY_ALPHA") %>%
  mutate(
    group_type = case_when(
      COUNTRY_ALPHA == "KOR" ~ "South Korea",
      COUNTRY_ALPHA == "TWN" ~ "Taiwan",
      COUNTRY_ALPHA == "IDN" ~ "Indonesia",
      COUNTRY_ALPHA == "MNG" ~ "Mongolia",
      COUNTRY_ALPHA == "PHL" ~ "Philippines",
      COUNTRY_ALPHA == "JPN" ~ "Japan",
      regime_category == "Liberal Democracy" ~ "Liberal Democracy",
      TRUE ~ "Other"
    ),
    Variable_Label = factor(
      Variable_Label,
      levels = c("Democracy Good", "Experts Rule", "Army Rule", "Strong Leader")
    )
  )

# Color Definitions (excluding Liberal Democracy from legend)
highlight_colors <- c(
  "South Korea" = "#e63946",
  "Taiwan"      = "#457b9d",
  "Indonesia"   = "#f4a261",
  "Mongolia"    = "#2a9d8f",
  "Philippines" = "#ffca3a",
  "Japan"       = "#f3722c"
)

# Plot

# First, set desired order (for legend)
proportions$group_type <- factor(
  proportions$group_type,
  levels = c(
    "Japan", "Philippines", "South Korea", "Taiwan", "Mongolia", "Indonesia",
    "Liberal Democracy", "Other"
  )
)

wvs_ea_all <- ggplot() +
  geom_line(
    data = proportions %>% filter(group_type == "Liberal Democracy"),
    aes(x = S020, y = Proportion, group = interaction(COUNTRY_ALPHA, Variable_Label)),
    color = "#64a3cb", size = 0.8, alpha = 0.6, show.legend = FALSE
  ) +
  geom_line(
    data = proportions %>% filter(group_type == "Other"),
    aes(x = S020, y = Proportion, group = interaction(COUNTRY_ALPHA, Variable_Label)),
    color = "lightgrey", size = 0.8, alpha = 0.3, show.legend = FALSE
  ) +
  geom_line(
    data = proportions %>% filter(group_type %in% names(highlight_colors)),
    aes(x = S020, y = Proportion, color = group_type, group = interaction(COUNTRY_ALPHA, Variable_Label)),
    size = 1.2
  ) +
  geom_point(
    data = proportions %>% filter(group_type %in% names(highlight_colors)),
    aes(x = S020, y = Proportion, color = group_type),
    size = 2
  ) +
  scale_color_manual(
  values = highlight_colors,
  breaks = c("Japan", "Philippines", "South Korea", "Taiwan", "Mongolia", "Indonesia")
) +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "Survey Year", y = "Proportion (%)") +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    strip.text = element_text(face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  facet_wrap(~Variable_Label)

#| label: fig-wvs-support
ggsave("figures/wvs_ea_all.pdf", plot = wvs_ea_all, device = "pdf", width = 10, height = 7, dpi = 300)


```

## V-dem (electoral)

```{r}


# Prepare V-Dem subset and relabel countries directly from country_name
vdem_cases <- vdem %>%
  filter(country_name %in% c("South Korea", "Taiwan", "Mongolia", "Indonesia", "Philippines", "Japan"),
         year >= 1945, year <= 2020) %>%
  select(COUNTRY = country_name, year, v2x_polyarchy) %>%
  mutate(COUNTRY = factor(COUNTRY, levels = c("Japan", "Philippines", "South Korea", "Taiwan", "Mongolia", "Indonesia")))

# Define highlight colors by country name in correct order
highlight_colors <- c(
  "Japan"       = "#f3722c",
  "Philippines" = "#ffca3a",
  "South Korea" = "#e63946",
  "Taiwan"      = "#457b9d",
  "Mongolia"    = "#2a9d8f",
  "Indonesia"   = "#f4a261"
)

# Generate electoral democracy plot
electoral_plot <- ggplot(vdem_cases, aes(x = year, y = v2x_polyarchy, color = COUNTRY)) +
  geom_line(size = 1.2) +
  scale_color_manual(values = highlight_colors) +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
  scale_x_continuous(breaks = seq(1945, 2020, by = 15)) +
  labs(
    x = "Year",
    y = "Electoral Democracy Index",
    color = ""
  ) +
  theme_light() +
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 9),
    axis.text.x = element_text(size = 8),
    axis.text.y = element_text(size = 8),
    plot.title = element_text(size = 12, face = "bold"),
    panel.grid.minor = element_blank()
  )

#| label: fig-vdem-plot
ggsave("figures/vdem_electoral_democracy.pdf", electoral_plot, width = 9, height = 5, dpi = 300)


```

## Guardianship support

```{r}

# Recode (drop cases that don't qualify as endorsements)
wvs_guardianship <- wvsdf %>%
  filter(S002VS >= 3) %>%
mutate(
  E114_pair = ifelse(!is.na(E114) & !is.na(E117), 
                     ifelse(E114 %in% c(1, 2) & E117 %in% c(1, 2), 1, 0), 
                     NA_real_),
  E115_pair = ifelse(!is.na(E115) & !is.na(E117), 
                     ifelse(E115 %in% c(1, 2) & E117 %in% c(1, 2), 1, 0), 
                     NA_real_),
  E116_pair = ifelse(!is.na(E116) & !is.na(E117), 
                     ifelse(E116 %in% c(1, 2) & E117 %in% c(1, 2), 1, 0), 
                     NA_real_)
)

# Summarise weighted proportions
wvs_guardianship <- wvs_guardianship %>%
  group_by(COUNTRY_ALPHA, S020) %>%
  summarise(
    Dahlian_Guardianship   = weighted.mean(E115_pair, w = S017, na.rm = TRUE),
    Strongman_Guardianship = weighted.mean(E114_pair, w = S017, na.rm = TRUE),
    Military_Guardianship  = weighted.mean(E116_pair, w = S017, na.rm = TRUE),
    Respondents = sum(!is.na(S017) & !is.na(E117)),  # Optional
    .groups = "drop"
  )

# Reshape to long format
guardianship_long <- wvs_guardianship %>%
  pivot_longer(
    cols = c("Dahlian_Guardianship", "Strongman_Guardianship", "Military_Guardianship"),
    names_to = "Measure", values_to = "Proportion"
  ) %>%
  filter(!is.na(Proportion) & Proportion > 0) %>%  # ✅ drop 0s and NAs
  mutate(
    Measure = recode(Measure,
      "Dahlian_Guardianship"   = "Dahlian Guardianship",
      "Strongman_Guardianship" = "Strongman Guardianship",
      "Military_Guardianship"  = "Military Guardianship"
    )
  )


# Add V-Dem regime classification
latest_year <- max(vdem$year, na.rm = TRUE)
vdem_classification <- vdem %>%
  filter(year == latest_year) %>%
  select(COUNTRY_ALPHA = country_text_id, country_name, v2x_regime) %>%
  mutate(regime_category = if_else(v2x_regime == 3, "Liberal Democracy", "Other"))

# Merge V-Dem classification
guardianship_long <- guardianship_long %>%
  left_join(vdem_classification, by = "COUNTRY_ALPHA") %>%
  mutate(
    group_type = case_when(
      COUNTRY_ALPHA == "KOR" ~ "South Korea",
      COUNTRY_ALPHA == "TWN" ~ "Taiwan",
      COUNTRY_ALPHA == "IDN" ~ "Indonesia",
      COUNTRY_ALPHA == "MNG" ~ "Mongolia",
      COUNTRY_ALPHA == "PHL" ~ "Philippines",
      COUNTRY_ALPHA == "JPN" ~ "Japan",
      regime_category == "Liberal Democracy" ~ "Liberal Democracy",
      TRUE ~ "Other"
    )
  )

# Define highlight ordering by most recent Strongman Guardianship level
focal_countries <- c("South Korea", "Taiwan", "Indonesia", "Mongolia", "Philippines")

highlight_order <- guardianship_long %>%
  filter(Measure == "Strongman Guardianship", group_type %in% focal_countries) %>%
  group_by(group_type) %>%
  filter(S020 == max(S020, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(desc(Proportion)) %>%
  pull(group_type)

highlight_order <- c(highlight_order, setdiff(focal_countries, highlight_order))

# Define custom colors
highlight_colors <- c(
  "South Korea" = "#e63946",
  "Taiwan"      = "#355d7f",   # distinguishable from liberal democracy
  "Indonesia"   = "#f4a261",
  "Mongolia"    = "#2a9d8f",
  "Philippines" = "#ffca3a",
  "Japan"       = "#f3722c"
)

# Plot guardianship measures with legend order in mind
guardianship_long$group_type <- factor(
  guardianship_long$group_type,
  levels = c("Japan", "Philippines", "South Korea", "Taiwan", "Mongolia", "Indonesia", "Liberal Democracy", "Other")
)


guardianship_types <- ggplot() +
  geom_line(
    data = guardianship_long %>% filter(group_type == "Liberal Democracy"),
    aes(x = S020, y = Proportion, group = interaction(COUNTRY_ALPHA, Measure)),
    color = "#64a3cb", size = 0.8, alpha = 0.6, show.legend = FALSE
  ) +
  geom_line(
    data = guardianship_long %>% filter(group_type == "Other"),
    aes(x = S020, y = Proportion, group = interaction(COUNTRY_ALPHA, Measure)),
    color = "lightgrey", size = 0.8, alpha = 0.3, show.legend = FALSE
  ) +
  geom_line(
    data = guardianship_long %>% filter(group_type %in% names(highlight_colors)),
    aes(x = S020, y = Proportion, color = group_type, group = interaction(COUNTRY_ALPHA, Measure)),
    size = 1.2
  ) +
  geom_point(
    data = guardianship_long %>% filter(group_type %in% names(highlight_colors)),
    aes(x = S020, y = Proportion, color = group_type),
    size = 2
  ) +
  scale_color_manual(
  values = highlight_colors,
  breaks = c("Japan", "Philippines", "South Korea", "Taiwan", "Mongolia", "Indonesia")
) +
  scale_y_continuous(labels = percent_format()) +
  labs(
    x = "Survey Year",
    y = "Proportion (%)"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    strip.text = element_text(face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  facet_wrap(~Measure)

#| label: fig-guardianship
ggsave("figures/guardianship_types.pdf", plot = guardianship_types, device = "pdf", width = 10, height = 7, dpi = 300)



```

## Generational analysis

```{r}

# Define generation cutoffs for each country
assign_generations <- function(df) {
  df %>%
    mutate(
      # Assign transition year by country
      Transition_Year = case_when(
        COUNTRY_ALPHA == "KOR" ~ 1987,
        COUNTRY_ALPHA == "TWN" ~ 1991,
        COUNTRY_ALPHA == "MNG" ~ 1992,
        COUNTRY_ALPHA == "IDN" ~ 1998,
        COUNTRY_ALPHA == "PHL" ~ 1986,
        COUNTRY_ALPHA == "JPN" ~ 1956,
        TRUE ~ NA_real_
      ),

      # Calculate age at the time of transition
      Transition_Age = Transition_Year - X002,

      # Assign generation based on age at transition
      Generation = case_when(
        Transition_Age >= 26 ~ "Authoritarian",   # Fully socialized pre-transition
        Transition_Age >= 18 & Transition_Age <= 25 ~ "Transitional",  # Political coming-of-age during transition
        Transition_Age < 18 ~ "Democratic",       # Socialized in post-transition democracy
        TRUE ~ NA_character_
      )
    )
}

# Preprocess and recode guardianship measures
age_breaks <- c(seq(18, 78, by = 5), Inf)
age_labels <- paste0(age_breaks[-length(age_breaks)], "–", age_breaks[-1] - 1)
age_labels[length(age_labels)] <- "79+"

wvs_generational <- wvsdf %>%
    filter(COUNTRY_ALPHA %in% c("KOR", "TWN", "MNG", "IDN", "PHL", "JPN")) %>%
    mutate(
        AGE = ifelse(!is.na(X003), X003, ifelse(!is.na(S020) & !is.na(X002), S020 - X002, NA)),
        AGE_BIN = cut(
            AGE,
            breaks = age_breaks,
            right = FALSE,
            include.lowest = TRUE,
            labels = age_labels
        ),

        E114_rec = ifelse(E114 %in% c(1, 2), 1, 0),  # Strong Leader
        E115_rec = ifelse(E115 %in% c(1, 2), 1, 0),  # Experts Rule
        E116_rec = ifelse(E116 %in% c(1, 2), 1, 0),  # Army Rule
        E117_rec = ifelse(E117 %in% c(1, 2), 1, 0)   # Democracy
    ) %>%
    assign_generations() %>%
    filter(!is.na(Generation), !is.na(AGE), AGE >= 18, AGE <= 100)

# Compute guardianship support by generation and age bin WITHOUT threshold restriction
wvs_gen_summary <- wvs_generational %>%
    group_by(COUNTRY_ALPHA, Generation, AGE_BIN) %>%
    summarise(
        n_dem = sum(S017[!is.na(E117)], na.rm = TRUE),
        n_dahl = sum(S017[!is.na(E117_rec) & !is.na(E115_rec)], na.rm = TRUE),
        n_strong = sum(S017[!is.na(E117_rec) & !is.na(E114_rec)], na.rm = TRUE),
        n_mil = sum(S017[!is.na(E117_rec) & !is.na(E116_rec)], na.rm = TRUE),

        Democracy = sum(E117_rec * S017, na.rm = TRUE) / n_dem,
        Dahlian = sum(E117_rec * E115_rec * S017, na.rm = TRUE) / n_dahl,
        Strongman = sum(E117_rec * E114_rec * S017, na.rm = TRUE) / n_strong,
        Military = sum(E117_rec * E116_rec * S017, na.rm = TRUE) / n_mil,
        .groups = "drop"
    ) %>%
    pivot_longer(cols = c("Democracy", "Dahlian", "Strongman", "Military"), names_to = "Measure", values_to = "Proportion") %>%
    filter(!is.na(Proportion), Proportion < 1, Proportion > 0) %>% ## to avoid plotting noise
    mutate(
        Measure = recode(Measure,
                         "Democracy" = "Democracy Good",
                         "Dahlian" = "Dahlian Guardianship",
                         "Strongman" = "Strongman Guardianship",
                         "Military" = "Military Guardianship"
        )
    )

# Plotting colors
generation_colors <- c(
    "Democratic" = "#e63946",
    "Transitional" = "#a8dadc",
    "Authoritarian" = "#1d3557"
)

# Reorder country presentation
wvs_gen_summary <- wvs_gen_summary %>%
  mutate(COUNTRY_ALPHA = factor(COUNTRY_ALPHA, levels = c(
    "JPN", "PHL", "KOR", "TWN", "MNG", "IDN"
  )))

# Plot
gen_guardianship <- ggplot(wvs_gen_summary, aes(x = AGE_BIN, y = Proportion, color = Generation, group = Generation)) +
    geom_line(linewidth = 1.2, na.rm = TRUE) +
    geom_point(size = 1.5, na.rm = TRUE) +
    facet_grid(COUNTRY_ALPHA ~ factor(Measure, levels = c("Democracy Good", "Dahlian Guardianship", "Military Guardianship", "Strongman Guardianship")), scales = "fixed", space = "free") +
    scale_color_manual(values = generation_colors, breaks = c("Democratic", "Transitional", "Authoritarian")) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 1)) +
    labs(
        #title = "Support for Guardianship Democracy by Political Generation",
        #subtitle = "% support for each system type, by generation and age at time of survey",
        x = "Age at Time of Survey (5-year bins)",
        y = "Proportion",
        color = ""
    ) +
    theme_light() +
    theme(
        strip.text = element_text(face = "bold"),
        axis.text.x = element_text(size = 7, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 7),
        legend.position = "bottom",
        panel.spacing.x = unit(c(1.25, 0.25, 0.25), "lines")
    )

#| label: fig-gen-plot
ggsave("figures/gen_guardianship.pdf", plot = gen_guardianship, device = "pdf", width = 12, height = 10, dpi = 300)


```


## Emancipative values

```{r}

### Emancipative values across democratic generations       
 
# Define countries and democratic generations
countries <- c("KOR", "TWN", "JPN", "IDN", "MNG", "DEU", "PHL")

democratic_generations <- list(
  KOR = 1970:2023,  # Transition in 1987 → born ≥1970
  TWN = 1969:2023,  # Transition in 1987 → born ≥1969
  JPN = 1938:2023,  # Postwar constitution in 1946 → age 18 by 1956 → born ≥1938
  IDN = 1981:2023,  # Transition in 1998 → born ≥1981
  MNG = 1973:2023,  # Transition in 1991 → born ≥1973
  PHL = 1970:2023,
  DEU = 1938:2023   # Basic Law (1949) → age 18 by 1956 → born ≥1938
)

# Filter and annotate democratic generation
wvs_eman <- wvsdf %>%
  filter(COUNTRY_ALPHA %in% countries) %>%
  mutate(
    AGE = ifelse(!is.na(X003), X003, ifelse(!is.na(S020) & !is.na(X002), S020 - X002, NA))
  ) %>%
  rowwise() %>%
  mutate(Democratic_Gen = case_when(
    COUNTRY_ALPHA == "KOR" & X002 %in% democratic_generations$KOR ~ TRUE,
    COUNTRY_ALPHA == "TWN" & X002 %in% democratic_generations$TWN ~ TRUE,
    COUNTRY_ALPHA == "JPN" & X002 %in% democratic_generations$JPN ~ TRUE,
    COUNTRY_ALPHA == "IDN" & X002 %in% democratic_generations$IDN ~ TRUE,
    COUNTRY_ALPHA == "MNG" & X002 %in% democratic_generations$MNG ~ TRUE,
    COUNTRY_ALPHA == "PHL" & X002 %in% democratic_generations$PHL ~ TRUE,
    COUNTRY_ALPHA == "DEU" & X002 %in% democratic_generations$DEU ~ TRUE,
    TRUE ~ FALSE
  )) %>%
  ungroup() %>%
  filter(Democratic_Gen, AGE >= 18 & AGE <= 100) %>%
  mutate(
  AGE_BIN = cut(
    AGE,
    breaks = seq(18, 98, by = 5),
    include.lowest = TRUE,
    right = FALSE,
    labels = paste(seq(18, 93, by = 5), seq(22, 97, by = 5), sep = "–")
  )
)

# Summarize by AGE_BIN and COUNTRY
emancipation_averages <- wvs_eman %>%
  group_by(COUNTRY_ALPHA, AGE_BIN) %>%
  summarise(
    Avg_Emancipation = weighted.mean(Y020, w = S017, na.rm = TRUE),
    Respondents = sum(!is.na(Y020)),
    .groups = "drop")

# Map country codes to names
country_names <- tibble::tibble(
  COUNTRY_ALPHA = c("KOR", "TWN", "JPN", "IDN", "MNG", "DEU", "PHL"),
  Country_Name = c("South Korea", "Taiwan", "Japan", "Indonesia", "Mongolia", "Germany", "Philippines")
)

emancipation_averages <- emancipation_averages %>%
  left_join(country_names, by = "COUNTRY_ALPHA")

# Determine emancipation averages as per regime type (V-dem)
regime_labels <- c(
  "Closed Autocracy", "Electoral Autocracy", "Electoral Democracy", "Liberal Democracy"
)

regime_averages <- wvsdf %>%
  left_join(vdem_classification, by = "COUNTRY_ALPHA") %>%
  filter(!is.na(Y020), !is.na(v2x_regime)) %>%
  group_by(v2x_regime) %>%
  summarise(
    Avg_Eman = weighted.mean(Y020, w = S017, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    Regime_Type = factor(v2x_regime, labels = regime_labels)
  )

# Define color palette
color_palette_eman <- c(
  "South Korea" = "#e63946",
  "Taiwan"      = "#457b9d",
  "Indonesia"   = "#f4a261",
  "Mongolia"    = "#2a9d8f",
  "Philippines" = "#ffca3a",
  "Japan"       = "#f3722c",  
  "Germany"     = "#984EA3"
)

# Full plot code: Emancipative values with interpretive thresholds and regime averages

# Combine Closed + Electoral Autocracy into one category
regime_averages_clean <- regime_averages %>%
  mutate(Regime_Group = case_when(
    v2x_regime %in% c(0, 1) ~ "Autocracy (Closed + Electoral)",
    v2x_regime == 2 ~ "Electoral Democracy",
    v2x_regime == 3 ~ "Liberal Democracy"
  )) %>%
  group_by(Regime_Group) %>%
  summarise(Avg_Eman = mean(Avg_Eman), .groups = "drop")

# Extract regime average y values
libdem_y <- regime_averages_clean %>% filter(Regime_Group == "Liberal Democracy") %>% pull(Avg_Eman)
electdem_y <- regime_averages_clean %>% filter(Regime_Group == "Electoral Democracy") %>% pull(Avg_Eman)
autocracy_y <- regime_averages_clean %>% filter(Regime_Group == "Autocracy (Closed + Electoral)") %>% pull(Avg_Eman)
yvals <- sort(c(autocracy_y, electdem_y, libdem_y))

# X position anchor for regime labels (adjust if needed)
label_x <- 10  # around the "68–72" bin

# Plot with legend order in mind
emancipation_averages$Country_Name <- factor(
  emancipation_averages$Country_Name,
  levels = c("Japan", "Philippines", "South Korea", "Taiwan", "Mongolia", "Indonesia", "Germany")
)


emancipation_plot <- ggplot(emancipation_averages,
                            aes(x = AGE_BIN, y = Avg_Emancipation, group = Country_Name, color = Country_Name)) +
  # Shaded bands with emphasis on middle segment
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = yvals[1], ymax = yvals[2],
           alpha = 0.08, fill = "white") +
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = yvals[2], ymax = yvals[3],
           alpha = 0.13, fill = "gray50") +
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = yvals[3],
           ymax = max(emancipation_averages$Avg_Emancipation, na.rm = TRUE),
           alpha = 0.08, fill = "white") +
  # Trend lines
  geom_line(size = 1.2) +
  geom_point(size = 2) +
  # Dotted regime average lines
  geom_hline(yintercept = autocracy_y, linetype = "dotted", color = "gray30", size = 0.5) +
  geom_hline(yintercept = electdem_y, linetype = "dotted", color = "gray30", size = 0.5) +
  geom_hline(yintercept = libdem_y, linetype = "dotted", color = "gray30", size = 0.5) +
  # Regime labels placed to the left (around AGE_BIN 68–72 marker)
  annotate("text", x = label_x, y = libdem_y + 0.01,
           label = paste0("Liberal Democracies (avg: ", round(libdem_y, 2), ")"),
           hjust = 0, size = 3.5, color = "gray20") +
  annotate("text", x = label_x, y = electdem_y + 0.01,
           label = paste0("Electoral Democracies (avg: ", round(electdem_y, 2), ")"),
           hjust = 0, size = 3.5, color = "gray20") +
  annotate("text", x = label_x, y = autocracy_y + 0.01,
           label = paste0("Autocracies (Electoral + Closed) (avg: ", round(autocracy_y, 2), ")"),
           hjust = 0, size = 3.5, color = "gray20") +
  # Labels and theme
  scale_color_manual(values = color_palette_eman) +
  labs(
    #title = "Emancipative Values Across Age Cohorts in Democratic Generations",
    #subtitle = "Weighted averages by 5-year age bins for East Asia and Germany",
    x = "Age at Time of Survey (5-year bins)",
    y = "Emancipative Values Index",
    color = ""
  ) +
  coord_cartesian(ylim = c(0.2, 0.8)) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    axis.title.x = element_text(size = 10),
    axis.title.y = element_text(size = 10),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8)
  )

#| label: fig-gen-eman-plot
ggsave("figures/democratic_generations_emancipation_plot.pdf", plot = emancipation_plot, device = "pdf", width = 10, height = 7, dpi = 300)


```
